I/O simulation model with Linux page cache, integration and evaluation in SimGrid framework

### 2020-07-24 paper_io_sim.tex
minor comment

            We separate our simulation model in two components, the IO
			Controller and the Memory Manager, which together simulate 
			file read/write mechanisms in Linux (Figure~\ref{fig:interaction}). 
			The Memory Manager simulates I/Os to cache, flushing, periodical flushing 
			and cache eviction, whereas the IO Controller simulates file reads and writes. 
			Simulated applications can simply interact with the IO Manager instead of 
			calling simulated storage directly as is the case with current simulators.

@@

	\section{Discussion and Future Work}
		\begin{itemize}
			\item Sensitivity of the simulator on the variation of memory and disk bandwidth. 
			\item Our model does not support random I/O and readahead.
		\end{itemize}
	\section{CFI for cluster}
\bibliographystyle{plain}
\bibliography{citation}

>>>>

            We separate our simulation model in two components, the IO
			Controller and the Memory Manager, which together simulate 
			file read/write mechanisms in Linux (Figure~\ref{fig:interaction}). 
			The Memory Manager simulates I/Os to cache, flushing, periodical flushing, 
			and cache eviction \tristan{how about periodical eviction?}, whereas the IO Controller simulates file reads and writes. 
			Simulated applications can simply interact with the IO Controller instead of 
			calling simulated storage directly as is the case with current simulators.

@@

	\section{Discussion and Future Work}
		\begin{itemize}
			\item Sensitivity of the simulator on the variation of memory and disk bandwidth. 
			\item Our model does not support random I/O and readahead.
			\item Disk state save/restore when hosts are turned on/off.
		\end{itemize}
	\section{CFI for cluster}
\bibliographystyle{plain}
\bibliography{citation}
